Designing a high-performance boundary element library with OpenCL and Numba

### 2021-05-28 main.tex
add bio

\begin{IEEEbiography}{Timo Betcke}{\,}is Professor of Computational Mathematics in the Department of Mathematics at University College London (UCL).
He originally studied Computational Engineering at Hamburg University of Technology before pursuing a DPhil in Numerical Analysis
at the University of Oxford, from which he graduated in 2006. Before joining UCL in 2011 he has held research positions at Braunschweig,
Manchester, and Reading. His work is on the interface of numerical analysis and computational sciences. He was principal investigator
in two EPSRC software infrastructure grants for the development of Bempp and has been PI and Co-I on a number of other projects related
to boundary element methods.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}{Timo Betcke}{\,}is Professor of Computational Mathematics in the Department of Mathematics at University College London (UCL).
He originally studied Computational Engineering at Hamburg University of Technology before pursuing a DPhil in Numerical Analysis
at the University of Oxford, from which he graduated in 2006. Before joining UCL in 2011 he held research positions at Braunschweig,
Manchester, and Reading. His work is on the interface of numerical analysis and computational sciences. He was principal investigator
in two EPSRC software infrastructure grants for the development of Bempp and has been PI and Co-I on a number of other projects related
to boundary element methods.
\end{IEEEbiography}

\begin{IEEEbiography}{Matthew W. Scroggs}{\,}is a postdoctoral research associate in the Department of Engineering at the
University of Cambridge, where he works on finite element methods and the open source finite element library FEniCSx.
Before moving to Cambridge, he obtained a PhD from the Department of Mathematics at University College London, where his
work focused on boundary element methods and Bempp.
\end{IEEEbiography}
